FLM for growth as function of SPEI

### 2020-10-30 R/vital rate models.Rmd
updating text and cleaning up code.

- ~~Take out saplings~~
- Separate models for CF and fragment
- Separate plots (models) for 2 shoots, 5 shoots
- Make presentation that describes DLNM for Maria
- Add random effects

@@

Take a crack at modeling height as a function of previous height and lagged, non-linear, SPEI.

@@

```{r}
g_df %>% 
  ggplot(aes(x = exp(x), y = exp(fit + coef(g_post_cf)[1]))) +
  geom_jitter(data = demog_full %>% filter(habitat %in% c("1-ha", "CF")),
              aes(x = shts, y = shts_next), alpha = 0.1) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = exp(fit + coef(g_post_cf)[1] - se),
                  ymax = exp(fit + coef(g_post_cf)[1] + se)),
              alpha = 0.2,
              fill = "blue") +
  labs(x = "size (#shoots)", y = "size (t + 1)") +
  facet_wrap(~habitat) +
  theme_bw() +
  plot_annotation(caption = "Note: these are from two separate models, not a size–habitat interaction!")
```
Plants don't grow much

```{r}
# anova(g_post_cf)
# anova(g_post_1ha)
```

@@

```{r}
s_df %>% 
  ggplot(aes(x = exp(x), y = plogis(fit + coef(s_post_cf)[1]))) +
  geom_line() +
  geom_ribbon(aes(ymin = plogis(fit + coef(s_post_cf)[1] - se),
                  ymax = plogis(fit + coef(s_post_cf)[1] + se)),
              alpha = 0.2) +
  labs(x = "size (#shoots)", y = "P(survival)") +
  facet_wrap(~habitat) +
  stat_summary_bin(data = demog_post %>% filter(habitat %in% c("1-ha", "CF")),
                   geom = "point",
                   fun = mean,
                   bins = 7,
                   aes(y = surv, x = shts)) +
  theme_bw() +
  plot_annotation(caption = "Note: these are from two separate models, not a size–habitat interaction!")
```

```{r}
# anova(s_post_cf)
# anova(s_post_1ha)
```

@@

I'm doubting things now because this makes it seem like the survival of an averaged sized plant (~2.3 shoots) is higher in fragments than in continuous forest.  I should really use an average sized plant in both habitats combined to get marginal effects.  Either way, the surface for 1-ha fragments is basically flat except for a slight *positive* effect of recent drought on survival.  In continuous forest, drought in the previous February and March has a negative impact on survival.  Wet conditions in the previous April–October have a positive effect on survival.

```{r}
demog_post %>% 
  ggplot(aes(surv)) +
  geom_bar(aes(y = stat(prop))) +
  facet_wrap(~habitat)

demog_post %>% 
  group_by(habitat) %>% 
  summarize(survived = sum(surv == 1, na.rm = TRUE),
            dead = sum(surv == 0, na.rm = TRUE),
            mean_shts = mean(shts, na.rm = TRUE)) %>% 
  mutate(p.surv = survived / (survived + dead))
```

>>>>

- ~~Remove seedlings from dataset, for now~~
- ~~Separate models for CF and fragment, for now~~
- Add model for probability of reproduction and other vital rates
- Model seedlings separately?
- Add random effects, interactions, other complexities
- Explore FGAM as alternative to DLNM (seems like they are doing the same thing, but maybe FGAM allows modeling of interactions?)

@@

Take a crack at modeling vital rates as a function of previous height and lagged, non-linear, SPEI.

@@

```{r}
g_df %>% 
  ggplot(aes(x = exp(x), y = exp(fit + coef(g_post_cf)[1]))) +
  geom_jitter(data = demog_full %>% filter(habitat %in% c("1-ha", "CF")),
              aes(x = shts, y = shts_next), alpha = 0.1) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = exp(fit + coef(g_post_cf)[1] - se),
                  ymax = exp(fit + coef(g_post_cf)[1] + se)),
              alpha = 0.2,
              fill = "blue") +
  labs(x = "size (#shoots)", y = "size (t + 1)") +
  facet_wrap(~habitat) +
  theme_bw() +
  plot_annotation(caption = "Note: these are from two separate models, not a size–habitat interaction!")
```
Plants don't grow much.

```{r}
anova(g_post_cf)
anova(g_post_1ha)
```

@@

```{r}
s_df %>% 
  ggplot(aes(x = exp(x), y = plogis(fit + coef(s_post_cf)[1]))) +
  geom_line() +
  geom_ribbon(aes(ymin = plogis(fit + coef(s_post_cf)[1] - se),
                  ymax = plogis(fit + coef(s_post_cf)[1] + se)),
              alpha = 0.2) +
  labs(x = "size (#shoots)", y = "P(survival)") +
  facet_wrap(~habitat) +
  stat_summary_bin(data = demog_post %>% filter(habitat %in% c("1-ha", "CF")),
                   geom = "point",
                   fun = mean,
                   bins = 20,
                   aes(y = surv, x = shts)) +
  theme_bw() +
  plot_annotation(caption = "Note: these are from two separate models, not a size–habitat interaction!")
```

```{r}
anova(s_post_cf)
anova(s_post_1ha)
```

@@

The surface for 1-ha fragments is basically flat except for a slight *negative* effect of recent wet weather on survival.  In continuous forest, drought in the previous February and March has a negative impact on survival.  Wet conditions or very dry conditions in the previous August–October have a positive effect on survival.
